Computer Science House Constitution

### 2025-06-09 constitution.tex

\asubsection{Active Membership Expectations}
Active Members are expected to be active participants in CSH as defined in \ref{Expectations of Active Members}.
Active Voting Members are expected to meet the requirements defined in \ref{Expectations of Voting Members}.

@@

\asubsection{Eligible Votes}
The number of Active Members eligible to vote on the issue.
The eligible voters for a vote are determined and fixed when the Voting Period begins.

>>>>

\asubsection{Active Membership Expectations}
Active Members are expected to be active participants in CSH as defined in \ref{Expectations of Active Members}.
Active Members are eligible to become Voting Members if they meet the requirements defined in \ref{Qualifications of Voting Members}.

@@

\asubsection{Eligible Votes}
The number of Active Members eligible to vote on the issue.
